%-------------------------
% Resume in Latex
% Author : Bilal Dawood
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[A4,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Bilal Dawood} \\ \vspace{1pt}
    \small +1 587-429-7635 $|$ \href{https://bilaldawood01.github.io}{\underline{Website}} $|$ 
    \href{https://linkedin.com/in/bilal-dawood-2021}{\underline{LinkedIn}} $|$
    \href{https://github.com/BilalDawood01}{\underline{Github}} $|$
\small{Calgary, AB}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Calgary}{Calgary, AB}
      {BSc in Electrical Engineering, Minor in Digital Engineering | GPA: 3.64}{Aug. 2019 -- May 2024}
  %  \resumeSubheading
  %    {Blinn College}{Bryan, TX}
   %   {Associate's in Liberal Arts}{Aug. 2014 -- May 2018}

   %%%%%%%% Relavent Coursework
   \begin{itemize}[leftmargin=0.0in, label={}]
    \small{\item{
     \textbf{Coursework and Certifications:}{ Application Specific Processors and Accelerators, Industrial IoT, Advanced ML and NN}
    }}
  \end{itemize}
  \resumeSubHeadingListEnd

  %-----------PROGRAMMING SKILLS----------- when CV ONLYYY
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
   \small{\item{
    \textbf{Languages}{: Java, Python, C/C++, MATLAB, JavaScript, HTML/CSS, Assembly (ARM, MIPS), Verilog} \\
    \textbf{Frameworks}{: React, Node.js, Flask, FastAPI, Tensorflow} \\
    \textbf{Developer Tools}{: Git, Gerrit, Linux, PuTTy, MS Azure, VS Code, PyCharm, Jira} \\
    \textbf{Design and Simulation}{: Cadence Allegro, MODELSIM, NI Multisim, PS:SE, Xilinx Vivado, Intel Quartus Prime, SIMULINK}\\
    \textbf{Hardware Tools}{: Oscilloscope, Spectrum Analyzer, Multimeter, Solder, Power Supplies, STM MCU, Pynq Z2 FPGA, PIC MCU}\\
    \textbf{Libraries}{: Pandas, NumPy, Matplotlib, Seaborn, Tkinter, Keras, OpenCV, Pillow, Scikit-learn}\\
    \textbf{Hobbies}{: Soccer, Badminton, Kick Boxing, Photography, Table Tennis}\\
   }}
\end{itemize}



\section{Key Courses}
\begin{itemize}[leftmargin=0.05in, label={}]
    \small{
    % Electrical Engineering
    \item \textbf{Electrical Engineering:}\\
    \begin{itemize}[leftmargin=0.15in, label={}]
        \item \textbf{Digital Circuits}{: Number systems, Boolean algebra, combinational and sequential circuits, counters, registers, and memory arrays.}\\
        \item \textbf{Digital Systems Design}{: Digital system design and testing, programmable technology, CAD tools, and design for testability.}\\
        \item \textbf{Digital Electronic Circuits}{: MOS transistor fundamentals, MOS logic gates, memory, and integrated circuit design.}\\
        \item \textbf{Analog Electronic Circuits}{: BJT amplifiers, operational amplifier circuits, power amplifiers.}\\
        \item \textbf{Circuits II}{: Laplace transforms, transfer functions, filter theory, transient responses, two-port circuits.}\\
        \item \textbf{Electromagnetic Waves and Applications}{: Wave propagation, transmission line theory, scattering parameters, waveguides.}\\
        \item \textbf{Power Systems Analysis}{: Power flow studies, stability, load frequency control, voltage control, power generation economics.}\\
        \item \textbf{Electrical Engineering Energy Systems}{: Power generation, transmission, distribution, three-phase systems, power flow analysis.}\\
        \item \textbf{Electronic Devices and Materials}{: Semiconductors, diodes, BJTs, MOSFETs, material properties.}\\
    \end{itemize}
    
    % Software Engineering
    \item \textbf{Software Engineering:}
    \begin{itemize}[leftmargin=0.15in, label={}]
        \item \textbf{Advanced Software Design and Development}{: Software modelling and design, object-oriented design, concurrent and database programming, systems integration.}\\
        \item \textbf{Advanced Applied AI and ML}{: Data extraction and visualization, learning algorithms, neural network architectures.}\\
        \item \textbf{Industrial IoT Systems and Data Analytics}{: IIoT fundamentals, digital frameworks, data analytics.}\\
        \item \textbf{Cyber-Physical Systems Engineering}{: Design, reliability, performance, security of cyber-physical systems, FSM design.}\\
        \item \textbf{Computer Organisation}{: CPU, memory, instruction sets, assembly language, virtual memory, I/O devices.}\\
        \item \textbf{Application Specific Processors and Accelerators}{: RISC, CISC, application-specific processors, hardware/software optimization, hardware-software co-design.}\\
    \end{itemize}
    
    % Telecommunications
    \item \textbf{Telecommunications:}\\
    \begin{itemize}[leftmargin=0.15in, label={}]
        \item \textbf{Signals and Transforms}{: Continuous and discrete-time signals, Fourier and Z-transforms, sampling theory.}\\
        \item \textbf{Communications Systems and Networks}{: Analog and digital communications, network protocol architectures, data/network security, performance analysis.}\\
    \end{itemize}
    
    % Control Systems
    \item \textbf{Control Systems:}\\
    \begin{itemize}[leftmargin=0.15in, label={}]
        \item \textbf{Control Systems I}{: Dynamic systems modeling, feedback control, transient and steady-state analysis, frequency response, compensation design.}\\
    \end{itemize}
    }
\end{itemize}




    %%%%% Important Courses: 
  % Digital Things: 
  % Digital circuits
  % Digital Systems Design 
  % Digital Electronic Circuits 
  % Computer Networks 

  % Software and AI: 
  % Advanced Software Design and Development
  % Advanced Applied Artificial Intelligence and Machine Learning 
  % Industrial IoT Systems and Data Analytics
  % Cyber-Physical Systems Engineering
  
  % Embedded:
  % Computer Organisation 
  % Application Specific Processors and Accelerators
  % Computer Networks 

  % Teleocm things:
  % Signals and Transforms
  % Circuits II
  % Analog Electronic Circuits
  % Electromagnetic Fields and Applications 
  % Introduction to Communications Systems and Networks 

  % Power Systems: 
  % Power Systems Analysis
  % Electrical Engineering Energy Systems 
  
  % Semis and Stuff:
  % Electronic Devices and Materials 
  % Digital Electronic Circuits 

  % Misc:
  % Control Systems I 
  % Microsoft Certified -- Fundamentals of Azure AI


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Digital Hardware Engineer (intern)}{May 2022 -- Aug 2023}
      {Ericsson Canada Inc}{Ottawa, ON}
      \resumeItemListStart
        \resumeItem{Achieved 70\% reduction in Thermal verification time by developing an automation tool using Python.} % python, automation, testing
        \resumeItem{Ensured accuracy by creating test cases and comparing recorded metrics manually with component datasheets.} %documentation, testing
        \resumeItem{Showcased report writing and presentation skills by preparing user manual and presenting results to management.} % documentation, presentation
        \resumeItem{Ensured electrical functionality by verifying power rail integrity on high voltage radio boards using Power Tree and multimeter.} %hardware skill
        \resumeItem{Conducted board bring-up and verification by identifying and recording Flash SPI timing parameters using Oscilloscope.} % hardware skill
        \resumeItem{Confirmed data transfer compliance by identifying and recording Flash SPI interface timing parameters using Oscilloscope.}
        \resumeItem{Supported PCB design verification using Cadence Allegro by leveraging existing radio board schematics.} % schematic designing
        \resumeItem{Hands on experience with UART, JTAG, I2C and SPI with Ericsson radio boards.} %hardware peripherals
        \resumeItem{Took initiative to update and fix faulty spectrum analyzer by working directly with hardware vendor.}
        \resumeItem{Power Rail Analysis using Power Tree and measuring continuity across capacitors to ensure no shorts were created.}
        \resumeItem{Leading research on high-frequency testing equipment, targeting optimal performance and value by comparing price with datasheet specifications and testing requirements.}
      \resumeItemListEnd
      
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------


    \resumeSubheading
      {Android SDK/NDK Full-Stack Developer (Intern)}{Feb 2023 -- Aug 2023}
      {Ericsson Canada Inc.}{Ottawa, ON}
      \resumeItemListStart
        \resumeItem{Enhanced backend data management by 57\% for application by creating 4 new classes and off-loading 80\% of the data.}
        \resumeItem{Increased UI functionality by incorporating filters.}
        % \resumeItem{Optimized app performance by reducing page load times by 90\% by replacing batch loading with infinite scrolling and removing redundant functions.}
        % \resumeItem{Reduced page load times by 90\% by optimizing app performance, showcasing expertise in software optimization.} % you can use this one or the one above.
        \resumeItem{Reduced page load times by 90\% by implementing infinite scrolling, showcasing expertise in software optimization.} % you can use this one or the one above
        \resumeItem{Collected and analyzed 5G performance metrics using Qualcomm Network Testing Device, contributing to app development.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

% %-----------LEADERSHIP EXPERIENCE-----------
\section{Leadership Experience}
 \resumeSubHeadingListStart

   \resumeSubheading
     {Treasurer}{Aug 2020 -- May 2022}
     {IEEE UofC Student Branch Executive Council}{Calgary, AB}
     \resumeItemListStart
       \resumeItem{Managed and maintained branch accounts for professional associations.}
       \resumeItem{Prepared and submitted Annual Budget reports and Financials.}
       \resumeItem{Developed financial strategies, ensured suitable funding for events, and advised on activity cost allocation.}
       \resumeItem{Presented data in a methodical format in front of other executive council members, demonstrating analytical thinking and proactive communication skills.}
     \resumeItemListEnd

   \resumeSubheading
     {Electrical Team Lead}{Sept 2021 -- Sept 2022}
     {Team Zeus}{Calgary, AB}
     \resumeItemListStart
       \resumeItem{Developed comprehensive and easily comprehendible documents for modifications on an electric motorcycle.}
       \resumeItem{Collaborated with other technical teams to integrate electrical systems into the vehicle.}
       \resumeItem{Performed multiple drafting tasks and ensured synchronous data-keeping for all electrical sub-teams.}
       \resumeItem{Assisted in designing and testing Battery Management System (BMS) and Electrical Control Unit (ECU).}
      %  \resumeItem{Applied practical experience in developing and testing Power Distribution Units (PDUs).}
       \resumeItem{Gained an understanding of principles of bike operation and learned about workshop safety practices.}
     \resumeItemListEnd
 \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
      {\textbf{Automated Transit Enforcement} $|$ \emph{Python, Git, Software Dev, Hardware Dev, OpenCV}}{Sept 2023 -- May 2024}
      \resumeItemListStart
        % \resumeItem{Improved transit efficiency by 13\% by leading the design and implementation of an automated enforcement prototype for Calgary Transit.}
        \resumeItem{Developed a comprehensive hardware block diagram to outline the integration and use of various components.} % hardware sourcing, designing and planning. 
        \resumeItem{Conducted research and selected hardware components based on literature review, electric ratings, and cost to select optimal components while ensuring functionality and compatability.}

        % The one below is 2 bullet points in one. 
        \resumeItem{Reduced power consumption by 36\% and memory utilization by 800\% by implementing efficient triggers for sensors (LiDAR, GPS, camera) using a Python script on an RPi running Linux.} % option 3
        % \resumeItem{Reduced power consumption by 36\% and memory utilization by 800\% by reading serial data from sensors (LiDAR, GPS, camera) and implementing efficient triggers with a Python script on an RPi running Linux.} % option 4 - longer description with more serial reading info
        % \resumeItem{Reduced power consumption by 36\% by developing a hardware proof-of-concept with Raspberry Pi and sensors (LiDAR, GPS, camera) to trigger recordings on Linux interface, which was transmitted and stored on the server.} % alternative 1
        % \resumeItem{Reduced power consumption by 36\% by developing a proof-of-concept with RPi and integrating LiDAR/GPS sensors through serial connections and GPIO pins} % alternative 2
        % \resumeItem{Reduced power consumption by 36\% by developing a proof-of-concept with RPi and sensors (LiDAR, GPS, camera)}
        \resumeItem{Reduced memory utilization and processing time by 800\% by setting appropriate triggers through embedded designing}
        \resumeItem{Integrated hardware components with the software server, ensuring smooth data transfer and system operation.} % hardware skill
        \resumeItem{Conducted extensive testing to ensure system reliability and performance under various operational conditions.} % hardware skill
        \resumeItem{Regularly shared progress with Calgary Transit, explaining tehcnical details in easy to undestand manner.}
        
        % \resumeItem{Realized 95\% license plate recognition accuracy by utilizing PaddleOCR for text detection and leveraging a cloud-based LPR API.}
        \resumeItem{Achieved 95\% license plate recognition accuracy using PaddleOCR and a cloud-based LPR API.} % more concise
        
        % \resumeItem{Achieved 93\% mAP vehicle and pedestrian detection by utilizing YOLOv8 object tracking model with data collected and labeled locally.}
        % \resumeItem{Designed and implemented SQLite database to store violation data and developed a graphical user interface for easy viewing and management of violations.}        
        \resumeItemListEnd

        \resumeProjectHeading
        {\textbf{Real-time Audio Filtering} $|$ \emph{C, ARM Assembly, STM MCU, Embedded Systems}}{Jan 2024 -- May 2024}
        \resumeItemListStart
          \resumeItem{Designed and implemented embedded real-time audio filter on the STM32F411 using C and ARM Assembly.}
          \resumeItem{Reduced filter sampling rate by 28\% and reduced program size by 13.6\% by utilizing optimization techniques involving block processing and use of ARM Assembly.}
          \resumeItem{Utilized Direct Memory Access (DMA) to efficiently load and verify audio files on MCU, ensuring accurate data extraction and processing.}
          \resumeItem{Implemented and compared various FIR filtering techniques (Circular Buffer, Block Processing).}
          \resumeItem{Compared performance (speed, memory usage) and verified integrity of filter using Python Notebook.}
          \resumeItem{Implemented Loop Unrolling and utilized architecture-specific SIMD instructions to meet audio timing requirements.}
          % \resumeItem{Created Python notebook to verify integrity of signal after filtering.}
        \resumeItemListEnd
        
        \resumeProjectHeading
        {\textbf{2D Image Convolution} $|$ \emph{C, Python, STM MCU, ARM Cortex-M4, DSP, Embedded Systems}}{Jan 2024 -- May 2024}
        \resumeItemListStart
          \resumeItem{Implemented various 2D Image filtering techniques using 3x3 kernels on STM32F411 using C.}
          \resumeItem{Loaded images to STM Microcontroller as binary file. Utilized convolution techniques to filter images.}
          % \resumeItem{Paid close attention to data access and boundary handling for image convolution.}
          \resumeItem{Displayed expertise with memory mapping by paying close attention to data access and boundary handling for image convolution.}
          \resumeItem{Implemented and observed the affect of various 3x3 kernels (edge filter, gaussian blur, sharpening).}
          \resumeItem{Created Python notebook to view images by decrypting binary file.}
          \resumeItem{Demonstrated expertise in digital signal processing and embedded systems.}
        \resumeItemListEnd

        \resumeProjectHeading
        {\textbf{Hardware Accelerator (Pynq-Z2 FPGA)} $|$ \emph{C, Xilinx Vitis HLS, FPGA, Python}}{Jan 2024 -- May 2024}
        \resumeItemListStart
          \resumeItem{Utilized AMD Xilinx Vitis High-Level-Synthesis (HLS) to build, synthesize and debug C code.}
          \resumeItem{Generated RTL designs and ensured proper resource utilization.}
          \resumeItem{Implemented hardware optimization techniques to improve performance of MAC operations on FPGA.}
          \resumeItem{Demonstrated proficiency with Loop Unrolling, Loop Fission and Pipelining optimization techniques on hardware.}
          \resumeItem{Conducted thorough testing and validation procedures using testbenches created in C as well as through C simulation and synthesis, to ensure functionality and performance of operations.}
          \resumeItem{Analyzed synthesis reports and utilized pragma directives to optimize loop latency, resource utilization and overall performance of hardware design.}
          \resumeItem{Contributed to the development of optimized hardware accelerators, enhancing processing efficiency and throughput for FPGA-based applications.}
          \resumeItem{Achieved 13\%-time reduction verified by exporting IP and generating bit-files to flash bitstreams to FPGA via Python notebook.}
        \resumeItemListEnd

        \resumeProjectHeading
        {\textbf{SolarCam} $|$ \emph{Embedded Systems, Solar Powered, C++}}{Jan 2022 -- May 2022}
        \resumeItemListStart
          \resumeItem{Developed an ESP32-microcontroller based solar powered security camera.}
          \resumeItem{Successfully sourced and integrated electrical components including solar panels, ESP32, PIR sensor, and camera module.}
          \resumeItem{Controlled GPIO pins using C++ to capture and save images.}
          \resumeItem{Designed a self-sustaining power system with solar charging, battery storage, and regulated voltage.}
          \resumeItem{Ensured adherence to relevant regulatory codes (ISO, CEC) for product quality, safety, and environmental considerations.}
        \resumeItemListEnd
        
        \resumeProjectHeading
        {\textbf{Deep learning Finger Digit Classifier GUI} $|$ \emph{Python, Machine Learning, GUI, Data Visualization}}{Jan 2022 -- May 2022}
        \resumeItemListStart
          \resumeItem{Developed a finger digits classifier with fastai and a CNN, achieving a significant accuracy boost from 60\% to 88\%.}
          \resumeItem{Employed data augmentation techniques to enhance real-time finger count prediction accuracy.}
          \resumeItem{Proficiently managed image data and analyzed model performance for thorough evaluation and refinement.}
          \resumeItem{Created a user-friendly GUI application and utilized Python libraries effectively for streamlined development and enhanced collaboration.}
          \resumeItem{Utilized Git for version control, maintaining a clean and organized codebase.}
          \resumeItem{Employed Seaborn and Matplotlib for data visualization, enhancing the presentation of results.}
        \resumeItemListEnd

        \resumeProjectHeading
        {\textbf{Yagi-Uda Antenna Design} $|$ \emph{Antenna Design, Signal Processing, Docuementation}}{March 2022 -- May 2022}
        \resumeItemListStart
          \resumeItem{Designed a Yagi-Uda antenna using copper wires and a split coaxial cable.}
          \resumeItem{Ensured optimal signal reception by achieving a power transfer of -20dB, indicating that ~1\% of power was reflected.}
          \resumeItem{Conducted experiments to measure the performance of the antenna under different conditions (materials, orientations).}
          \resumeItem{Used RTL-SDR USB radio devices and software to measure and analyze signal outputs.}
          \resumeItem{Identified and resolved issues during the design and testing phases of the antenna project, such as signal interference.}
          \resumeItem{Ensured precision in component measurements and soldering to achieve desired signal reception and circuit performance.}
          \resumeItem{Documented the design, methodology, results, and analysis of the projects in detailed reports.}
          \resumeItem{Tested the antenna with various materials between the transmitting and receiving antennas, demonstrating robustness and adaptability to different environmental conditions.}
          \resumeItem{Used RTL-SDR USB for receiving and demodulating audio signals, and measuring signal outputs under various conditions}
        \resumeItemListEnd
        
        \resumeProjectHeading
        {\textbf{AM Receiver System Desing} $|$ \emph{Circuit Design and Analysis, Multisim, Simulation}}{Oct 2021 -- Dec 2021}
        \resumeItemListStart
          \resumeItem{Designed and implemented an AM receiver system.}
          \resumeItem{Developed active filter and base-band amplifier circuits.}
          \resumeItem{Used parametric sweeps and AC analysis to optimize circuit performance.}
          \resumeItem{Analyzed signals at different points in the AM receiver circuit to ensure proper reception and demodulation.}
          \resumeItem{Used simulation software (NI Multisim) to verify theoretical calculations and optimize circuit designs.}
          \resumeItem{Documented the design, methodology, results, and analysis of the projects in detailed reports.}
          \resumeItem{Utilized for DC and AC analysis, including tools like Multisim or similar simulation platforms for parametric sweeps and small-signal analysis.}
        \resumeItemListEnd
  
        \resumeProjectHeading
        {\textbf{Altera DE10-Lite Distance Sensor} $|$ \emph{VHDL, Intel Quartus Prime, MODELSIM, FPGA}}{Sept 2021 -- Dec 2021}
        \resumeItemListStart
          \resumeItem{Implemented voltage-to-distance conversion in VHDL using Intel Quartus Prime.}
          \resumeItem{Design and implementation met timing requirements for digital signal processing.}
          \resumeItem{Created testbenches to conduct tests and simulate digital signals and switch gates to be verified using MODELSIM.}
          \resumeItem{Configured DE10 display for distance/voltage based on switch state.}
          \resumeItem{Demonstrated proficiency in FPGA programming, sensor integration, and VHDL, highlighting skills in hardware design and testing.}
          \resumeItem{Generated RTL schematic to view flow of bits.}
        \resumeItemListEnd
        
        \resumeProjectHeading
        {\textbf{Point Based Graphical Zoom} $|$ \emph{MATLAB, Graphical User Interface, Image Processing}}{July 2021 -- July 2021}
        \resumeItemListStart
          \resumeItem{Used MATLAB to create a graphical point-based zoom function.}
          \resumeItem{The function generated a bounding box and produced a new figure based on any two points on a MATLAB-produced graph.}
        \resumeItemListEnd

        \resumeProjectHeading
        {\textbf{UnderPressure Posture Corrector} $|$ \emph{C++, Embedded Systems, Agile, Product Development}}{Jan 2021 -- May 2021}
        \resumeItemListStart
          \resumeItem{Developed an Arduino-based posture corrector using an Arduino Nano, resistive strips, and a speaker.}
          \resumeItem{Applied voltage dividers and utilized C++ and Arduino IDE for embedded programming.}
          \resumeItem{Implemented Agile project management methodologies (sprint and scrum) for efficient development.}
          \resumeItem{Received awards for "Most Innovative Product," "Best Marketing," and "Best Use of Humor."}
        \resumeItemListEnd

        
        \resumeProjectHeading
        {\textbf{DFF Synchronous Sequential Circuit} $|$ \emph{Simulation, Analysis, Digital logic Design}}{Nov 2020 -- Dec 2020}
        \resumeItemListStart
          \resumeItem{Implemented d-latches and d-flip-flops using Quartus for simulation and verification.}
          \resumeItem{Designed a synchronous detector circuit, creating state transition diagrams and K-maps to define behavior.}
          \resumeItem{Developed a clock divider to manage timing requirements within digital circuits.}
          \resumeItem{Utilized Intel Quartus Prime for designing, simulating and verifying digital circuits.}
          \resumeItem{Utilized K-maps to simplify logic desing.}
          \resumeItem{Ensured accurate operation of digital components, with the synchronous detector circuit correctly identifying the binary sequences}
          \resumeItem{Simplified logical expressions from K-maps to enhance circuit efficiency, demonstrating advanced problem-solving skills.}
        \resumeItemListEnd

        \resumeProjectHeading
        {\textbf{C++ Flight Management Program} $|$ \emph{C++, File Handling, Algorithm, Software Development}}{June 2020 -- July 2020}
        \resumeItemListStart
          \resumeItem{Developed and implemented a Flight Management Program in C++, incorporating classes for Flight, Passenger, and Seat.}
          \resumeItem{Utilized file handling to read and process flight information from a text file, showcasing proficiency in data input/output operations.}
          \resumeItem{Implemented functionalities such as displaying seat maps, managing passenger information, adding/removing passengers, and saving data to enhance the program's usability.}
          \resumeItem{Applied the Selection Sort algorithm for efficient organization of passenger data based on seat locations, demonstrating algorithmic problem-solving skills.}
        \resumeItemListEnd
  
        \resumeProjectHeading
        {\textbf{Impact of Green Line LRT Research Project} $|$ \emph{Research, Analysis, Presentation}}{July 2020 -- Aug 2020}
        \resumeItemListStart
          \resumeItem{Researched and wrote a report on the impact of the Green Line LRT and its stations on stakeholders.}
          \resumeItem{Analyzed stakeholders, including the public, residents near the station, taxpayers, and Calgary Transit employees.}
          \resumeItem{Considered financial restrictions and proposed solutions to potential problems.}
          \resumeItem{Gave a professional and technical presentation summarizing findings.}
        \resumeItemListEnd
        
        \resumeProjectHeading
        {\textbf{Calgary Weather Data Visualization} $|$ \emph{Java, GUI, Data Visualization}}{Nov 2019 -- Dec 2019}
        \resumeItemListStart
          \resumeItem{Implemented a GUI and user-interactive program using Java-based Language Processing.}
          \resumeItem{Displayed daily average minimum and maximum temperature data for the last 30 years in Calgary.}
          \resumeItem{Enabled user flexibility in selecting data for specific months and displaying maximum or minimum temperatures.}
        \resumeItemListEnd

      \resumeSubHeadingListEnd  
        



%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Java, Python, C/C++, MATLAB, JavaScript, HTML/CSS, Assembly (ARM, MIPS), Verilog} \\
     \textbf{Frameworks}{: React, Node.js, Flask, FastAPI, Tensorflow} \\
     \textbf{Developer Tools}{: Git, Gerrit, Linux, PuTTy, MS Azure, VS Code, PyCharm, Jira} \\
     \textbf{Design and Simulation}{: Cadence Allegro, MODELSIM, NI Multisim, PS:SE, Xilinx Vivado, Intel Quartus Prime, SIMULINK}\\
     \textbf{Hardware Tools}{: Oscilloscope, Spectrum Analyzer, Multimeter, Solder, Power Supplies, STM MCU, Pynq Z2 FPGA, PIC MCU}\\
     \textbf{Libraries}{: Pandas, NumPy, Matplotlib, Seaborn, Tkinter, Keras, OpenCV, Pillow, Scikit-learn}\\
     \textbf{Hobbies}{: Soccer, Badminton, Kick Boxing, Photography, Table Tennis}\\
    }}
 \end{itemize}

 %-----------Awards-----------
\section{Awards}
% \resumeItemListStart
%     \resumeItem{Jason Lang Scholarship (2020,2021,2023), Dean's List (2020, 2021, 2024)}
%  \resumeItemListEnd
 \begin{itemize}[leftmargin=0.15in, label={}]
  \small{\item{
   \textbf{Jason Lang Scholarship}{(2020, 2021, 2023),} \textbf{Dean's List}{(2020, 2021, 2024)}
  }}
\end{itemize}

%-------------------------------------------
\end{document}
