% Bilal Dawood Entry-Level Cover Letter Template

%%%%%%% --------------------------------------------------------------------------------------
%%%%%%%  STARTING HERE, DO NOT TOUCH ANYTHING 
%%%%%%% --------------------------------------------------------------------------------------

%%%% Define Document type
\documentclass[11pt,a4]{article}

%%%% Include Packages
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
 \usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{multicol}
\usepackage{hyperref}
\usepackage{csquotes}
\usepackage{tabularx}
\hypersetup{colorlinks=true,urlcolor=black}
\usepackage[11pt]{moresize}
\usepackage{setspace}
\usepackage{fontspec}
\usepackage[inline]{enumitem}
\usepackage{ragged2e}
\usepackage{anyfontsize}

%%%% Set Margins
\usepackage[margin=1cm]{geometry}

%%%% Set Fonts
% \setmainfont[
% BoldFont=SourceSansPro-Semibold.otf,
% ItalicFont=SourceSansPro-RegularIt.otf
% ]{SourceSansPro-Regular.otf}
\usepackage{mathpazo}

%%%% Set Page Style
\pagestyle{fancy}
\fancyhf{} 
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

%%%% Set URL Style
\urlstyle{same}

%%%% Set Indentation
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

%%%% Set Secondary Color, Page Number Color, Footer Text
\definecolor{UI_blue}{RGB}{32, 64, 151}
\definecolor{HF_color}{RGB}{179, 179, 179}
\rfoot{{\color{HF_color} \thepage \ of \ 1, Updated \today}}

%%%% Set Heading Format
\titleformat{\section}{
\color{UI_blue} \scshape \raggedright \large 
}{}{0em}{}[\vspace{-0.7cm} \hrulefill \vspace{-0.2cm}]
%%%%%%% --------------------------------------------------------------------------------------
%%%%%%% --------------------------------------------------------------------------------------
%%%%%%%  END OF "DO NOT TOUCH" REGION
%%%%%%% --------------------------------------------------------------------------------------
%%%%%%% --------------------------------------------------------------------------------------


\begin{document}

%%%%%%% --------------------------------------------------------------------------------------
%%%%%%%  HEADER
%%%%%%% --------------------------------------------------------------------------------------
\begin{center}
    \begin{minipage}[b]{0.24\textwidth}
            \large +1 587-429-7635 \\
            \large \href{mailto:bilaldawood099@outlook.com}{\underline{bilaldawood099@outlook.com}} 
    \end{minipage}% 
    \begin{minipage}[b]{0.5\textwidth}
            \centering
            {\Huge Bilal Dawood} \\ %
            \vspace{0.1cm}
            {\color{UI_blue} \Large{Hardware Engineer}} \\
    \end{minipage}% 
    \begin{minipage}[b]{0.24\textwidth}
            \flushright \large
            {\href{https://linkedin.com/in/bilal-dawood-2021}{\underline{LinkedIn}} } \\
            \href{https://bilaldawood01.github.io}{\underline{Portfolio}}
    \end{minipage}   
    
\vspace{-0.15cm} 
{\color{UI_blue} \hrulefill}
\end{center}

\justify
\setlength{\parindent}{0pt}
\setlength{\parskip}{12pt}
\vspace{0.2cm}
\begin{center}
    {\color{UI_blue} \Large{COVER LETTER}}
\end{center}


%%%%%%% --------------------------------------------------------------------------------------
%%%%%%%  First 2 Lines
%%%%%%% --------------------------------------------------------------------------------------

Date: \today \par \vspace{-0.1cm}
Dear Hiring Manager,

I am writing to express my strong interest in the Hardware Engineer position at Schweitzer Engineering Laboratories (SEL). As a recent graduate with a BSc in Electrical Engineering from the University of Calgary, I am excited about the opportunity to contribute to SEL's mission of developing critical devices for power systems and infrastructure.

My academic background and internship experiences have prepared me well for this role. During my internship at Ericsson Canada Inc., I gained hands-on experience in verifying digital circuit designs using Cadence Allegro and working with various communication protocols such as UART, JTAG, I2C, and SPI. This experience aligns closely with SEL's focus on developing reliable communication and control devices for the power grid. Additionally, my coursework in Analog Electronic Circuits, Digital Electronic Circuits, and Electrical Engineering Energy Systems has given me a strong foundation in the principles that underpin SEL's products.

I am particularly drawn to SEL's commitment to manufacturing high-quality components in-house. My experience as an Electrical Team Lead for Team Zeus, where I worked on electric motorcycle systems, has honed my skills in integrating electrical systems and collaborating across technical teams. This experience, combined with my academic projects such as designing an AM receiver system and developing an automated transit enforcement system, has given me practical experience in circuit design, system design, and electromagnetic compatibility – all key areas emphasized in your job description.

The opportunity to design and test devices that prevent blackouts and enhance the reliability of power systems is both challenging and deeply motivating to me. I am confident in my ability to analyze, design, and develop circuits, as well as prepare and maintain detailed documentation, as required for this role.

Thank you for considering my application. I am eager to bring my technical skills, passion for innovation, and commitment to quality to the Hardware Engineer role at SEL. I look forward to the opportunity to discuss how I can contribute to your team's success.

%%%%%%% --------------------------------------------------------------------------------------
%%%%%%%  SIGNATURE
%%%%%%% --------------------------------------------------------------------------------------

\vspace{0.5cm}
\raggedright
Sincerely, \\ Bilal Dawood \\ +1 587-429-7635 \\ \href{mailto:bilaldawood099@outlook.com}{\underline{bilaldawood099@outlook.com}}

\end{document}